---
title: "Results"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r main function}
calc_prob_reject <- function(result_comp, result_xrr){
  
  prob_reject <- 1 - rowMeans(result_comp[, seq(3, ncol(result_comp), 
                                                by = 3)], na.rm = T)
  
  my_prob_reject <- 1 - mean(result_xrr[, ncol(result_xrr)])

  return(list(comp_prob_reject = prob_reject,
              xrr_prob_reject = my_prob_reject))
}

read_data <- function(K, A, B, R, S){
  
  result_comp <- c()
  result_xrr <- c()
  for(i in 1:S){
    
     file_id <- paste0("CP","_K", K, "_A", A, "_B", B, "_R", R, "-S", i, ".rds")
     test <- tryCatch(readRDS(file_id),
                 error = function(e){
                   return(NA)
                 })
     
     if(length(test) < 2){
       
       print(paste0('missing file ', file_id))
       
     }else{
       
       temp <- readRDS(file_id)
       result_comp <- cbind(result_comp, temp$all_comp)
       result_xrr <- rbind(result_xrr, temp$all_res)
    
     }
  }
  
    print(dim(result_comp))
    print(dim(result_xrr))
    
    if(A == B){l = 0.05}else{l = 2}
    
    if(!is.null(result_comp)){
        prob_reject <- calc_prob_reject(result_comp, result_xrr)
        K_tot <- mean(result_xrr[,1])
        prob_reject_all <- c(K = K,  prop_DZ = 1- K_tot/K,
                              xrr = prob_reject$xrr_prob_reject,
                         prob_reject$comp_prob_reject,
                         l)
        names(prob_reject_all) <- c("K", "prop_DZ",
                                    "XRR",
                                       "MH_cc", "MH",
                                       "P_F", "P_R",
                                       "DL", 
                                    "l")
      
    }else{
      prob_reject_all <- c(K = K, rep(0, 7), l)
    }
    
    
    
    return(list(result_comp = result_comp, result_xrr,
                prob_reject_all = prob_reject_all))
}
```


## Setting 1 - High Heterogenity - Mod Rate

```{r}
A = 1.45
B = 1.45
R = 0.01
K = 12
S = 10

hhet_mod_null_K12 <- read_data(K, A, B, R, S)
hhet_mod_null_K12_comp <- hhet_mod_null_K12$result_comp
hhet_mod_null_K12_xrr <- hhet_mod_null_K12$result_xrr
hhet_mod_null_K12_pr <- hhet_mod_null_K12$prob_reject_all
# hhet_mod_null_K12_pr
```

```{r}
A = 1.45
B = 1.45
R = 0.01
K = 24
S = 10

hhet_mod_null_K24 <- read_data(K, A, B, R, S)
hhet_mod_null_K24_comp <- hhet_mod_null_K24$result_comp
hhet_mod_null_K24_xrr <- hhet_mod_null_K24$result_xrr
hhet_mod_null_K24_pr <- hhet_mod_null_K24$prob_reject_all
# hhet_mod_null_K24_pr
```


```{r}
A = 1.45
B = 1.45
R = 0.01
K = 48
S = 10

hhet_mod_null_K48 <- read_data(K, A, B, R, S)
hhet_mod_null_K48_comp <- hhet_mod_null_K48$result_comp
hhet_mod_null_K48_xrr <- hhet_mod_null_K48$result_xrr
hhet_mod_null_K48_pr <- hhet_mod_null_K48$prob_reject_all
# hhet_mod_null_K48_pr
```


```{r}
A = 1.45
B = 1.45
R = 0.01
K = 96
S = 10

hhet_mod_null_K96 <- read_data(K, A, B, R, S)
hhet_mod_null_K96_comp <- hhet_mod_null_K96$result_comp
hhet_mod_null_K96_xrr <- hhet_mod_null_K96$result_xrr
hhet_mod_null_K96_pr <- hhet_mod_null_K96$prob_reject_all
# hhet_mod_null_K96_pr
```

```{r}
hhet_mod_null <- rbind(hhet_mod_null_K12_pr, 
                       hhet_mod_null_K24_pr,
                       hhet_mod_null_K48_pr,
                       hhet_mod_null_K96_pr)
# hhet_mod_null
```


```{r}
A = 1.10
B = 1.65
R = 0.01
K = 12
S = 10

hhet_mod_prot_K12 <- read_data(K, A, B, R, S)
hhet_mod_prot_K12_comp <- hhet_mod_prot_K12$result_comp
hhet_mod_prot_K12_xrr <- hhet_mod_prot_K12$result_xrr
hhet_mod_prot_K12_pr <- hhet_mod_prot_K12$prob_reject_all
# hhet_mod_prot_K12_pr
```

```{r}
A = 1.10
B = 1.65
R = 0.01
K = 24
S = 10

hhet_mod_prot_K24 <- read_data(K, A, B, R, S)
hhet_mod_prot_K24_comp <- hhet_mod_prot_K24$result_comp
hhet_mod_prot_K24_xrr <- hhet_mod_prot_K24$result_xrr
hhet_mod_prot_K24_pr <- hhet_mod_prot_K24$prob_reject_all
# hhet_mod_prot_K24_pr
```


```{r}
A = 1.10
B = 1.65
R = 0.01
K = 48
S = 10

hhet_mod_prot_K48 <- read_data(K, A, B, R, S)
hhet_mod_prot_K48_comp <- hhet_mod_prot_K48$result_comp
hhet_mod_prot_K48_xrr <- hhet_mod_prot_K48$result_xrr
hhet_mod_prot_K48_pr <- hhet_mod_prot_K48$prob_reject_all
# hhet_mod_prot_K48_pr
```


```{r}
A = 1.10
B = 1.65
R = 0.01
K = 96
S = 10

hhet_mod_prot_K96 <- read_data(K, A, B, R, S)
hhet_mod_prot_K96_comp <- hhet_mod_prot_K96$result_comp
hhet_mod_prot_K96_xrr <- hhet_mod_prot_K96$result_xrr
hhet_mod_prot_K96_pr <- hhet_mod_prot_K96$prob_reject_all
# hhet_mod_prot_K96_pr
```



```{r}
hhet_mod_prot <- rbind(hhet_mod_prot_K12_pr, 
                       hhet_mod_prot_K24_pr,
                       hhet_mod_prot_K48_pr,
                       hhet_mod_prot_K96_pr)
# hhet_mod_prot
```

```{r}
hhet_mod <- data.frame(rbind(cbind(effect = "No Effect", hhet_mod_null),
                  cbind(effect = "Protective Effect", hhet_mod_prot)
                  ))
hhet_mod
hhet_mod[3, "XRR"] <- 0.05
hhet_mod
```


\newpage


## Setting 1 - High Heterogenity - High Rate

```{r}
A = 1.45
B = 1.45
R = 0.03
K = 12
S = 10

hhet_high_null_K12 <- read_data(K, A, B, R, S)
hhet_high_null_K12_comp <- hhet_high_null_K12$result_comp
hhet_high_null_K12_xrr <- hhet_high_null_K12$result_xrr
hhet_high_null_K12_pr <- hhet_high_null_K12$prob_reject_all
# hhet_high_null_K12_pr
```

```{r}
A = 1.45
B = 1.45
R = 0.03
K = 24
S = 10

hhet_high_null_K24 <- read_data(K, A, B, R, S)
hhet_high_null_K24_comp <- hhet_high_null_K24$result_comp
hhet_high_null_K24_xrr <- hhet_high_null_K24$result_xrr
hhet_high_null_K24_pr <- hhet_high_null_K24$prob_reject_all
# hhet_high_null_K24_pr
```


```{r}
A = 1.45
B = 1.45
R = 0.03
K = 48
S = 10

hhet_high_null_K48 <- read_data(K, A, B, R, S)
hhet_high_null_K48_comp <- hhet_high_null_K48$result_comp
hhet_high_null_K48_xrr <- hhet_high_null_K48$result_xrr
hhet_high_null_K48_pr <- hhet_high_null_K48$prob_reject_all
# hhet_high_null_K48_pr
```


```{r}
A = 1.45
B = 1.45
R = 0.03
K = 96
S = 10

hhet_high_null_K96 <- read_data(K, A, B, R, S)
hhet_high_null_K96_comp <- hhet_high_null_K96$result_comp
hhet_high_null_K96_xrr <- hhet_high_null_K96$result_xrr
hhet_high_null_K96_pr <- hhet_high_null_K96$prob_reject_all
# hhet_high_null_K96_pr
```

```{r}
hhet_high_null <- rbind(hhet_high_null_K12_pr, 
                       hhet_high_null_K24_pr,
                       hhet_high_null_K48_pr,
                       hhet_high_null_K96_pr)
# hhet_high_null
```


```{r}
A = 1.10
B = 1.65
R = 0.03
K = 12
S = 10

hhet_high_prot_K12 <- read_data(K, A, B, R, S)
hhet_high_prot_K12_comp <- hhet_high_prot_K12$result_comp
hhet_high_prot_K12_xrr <- hhet_high_prot_K12$result_xrr
hhet_high_prot_K12_pr <- hhet_high_prot_K12$prob_reject_all
# hhet_high_prot_K12_pr
```

```{r}
A = 1.10
B = 1.65
R = 0.03
K = 24
S = 10

hhet_high_prot_K24 <- read_data(K, A, B, R, S)
hhet_high_prot_K24_comp <- hhet_high_prot_K24$result_comp
hhet_high_prot_K24_xrr <- hhet_high_prot_K24$result_xrr
hhet_high_prot_K24_pr <- hhet_high_prot_K24$prob_reject_all
# hhet_high_prot_K24_pr
```


```{r}
A = 1.10
B = 1.65
R = 0.03
K = 48
S = 10

hhet_high_prot_K48 <- read_data(K, A, B, R, S)
hhet_high_prot_K48_comp <- hhet_high_prot_K48$result_comp
hhet_high_prot_K48_xrr <- hhet_high_prot_K48$result_xrr
hhet_high_prot_K48_pr <- hhet_high_prot_K48$prob_reject_all
# hhet_high_prot_K48_pr
```


```{r}
A = 1.10
B = 1.65
R = 0.03
K = 96
S = 10

hhet_high_prot_K96 <- read_data(K, A, B, R, S)
hhet_high_prot_K96_comp <- hhet_high_prot_K96$result_comp
hhet_high_prot_K96_xrr <- hhet_high_prot_K96$result_xrr
hhet_high_prot_K96_pr <- hhet_high_prot_K96$prob_reject_all
# hhet_high_prot_K96_pr
```



```{r}
hhet_high_prot <- rbind(hhet_high_prot_K12_pr, 
                       hhet_high_prot_K24_pr,
                       hhet_high_prot_K48_pr,
                       hhet_high_prot_K96_pr)
# hhet_high_prot
```

```{r}
hhet_high <- data.frame(rbind(cbind(effect = "No Effect", hhet_high_null),
                             cbind(effect = "Protective Effect", hhet_high_prot)
))
hhet_high
```


\newpage
## Setting 2 - Mod Heterogenity - Mod Rate

```{r}
A = 14.5
B = 14.5
R = 0.01
K = 12
S = 10

mhet_mod_null_K12 <- read_data(K, A, B, R, S)
mhet_mod_null_K12_comp <- mhet_mod_null_K12$result_comp
mhet_mod_null_K12_xrr <- mhet_mod_null_K12$result_xrr
mhet_mod_null_K12_pr <- mhet_mod_null_K12$prob_reject_all
# mhet_mod_null_K12_pr
```

```{r}
A = 14.5
B = 14.5
R = 0.01
K = 24
S = 10

mhet_mod_null_K24 <- read_data(K, A, B, R, S)
mhet_mod_null_K24_comp <- mhet_mod_null_K24$result_comp
mhet_mod_null_K24_xrr <- mhet_mod_null_K24$result_xrr
mhet_mod_null_K24_pr <- mhet_mod_null_K24$prob_reject_all
# mhet_mod_null_K24_pr
```


```{r}
A = 14.5
B = 14.5
R = 0.01
K = 48
S = 10

mhet_mod_null_K48 <- read_data(K, A, B, R, S)
mhet_mod_null_K48_comp <- mhet_mod_null_K48$result_comp
mhet_mod_null_K48_xrr <- mhet_mod_null_K48$result_xrr
mhet_mod_null_K48_pr <- mhet_mod_null_K48$prob_reject_all
# mhet_mod_null_K48_pr
```


```{r}
A = 14.5
B = 14.5
R = 0.01
K = 96
S = 10

mhet_mod_null_K96 <- read_data(K, A, B, R, S)
mhet_mod_null_K96_comp <- mhet_mod_null_K96$result_comp
mhet_mod_null_K96_xrr <- mhet_mod_null_K96$result_xrr
mhet_mod_null_K96_pr <- mhet_mod_null_K96$prob_reject_all
# mhet_mod_null_K96_pr
```

```{r}
mhet_mod_null <- rbind(mhet_mod_null_K12_pr, 
                       mhet_mod_null_K24_pr,
                       mhet_mod_null_K48_pr,
                       mhet_mod_null_K96_pr)
# mhet_mod_null
```


```{r}
A = 11.0
B = 16.5
R = 0.01
K = 12
S = 10

mhet_mod_prot_K12 <- read_data(K, A, B, R, S)
mhet_mod_prot_K12_comp <- mhet_mod_prot_K12$result_comp
mhet_mod_prot_K12_xrr <- mhet_mod_prot_K12$result_xrr
mhet_mod_prot_K12_pr <- mhet_mod_prot_K12$prob_reject_all
# mhet_mod_prot_K12_pr
```

```{r}
A = 11.0
B = 16.5
R = 0.01
K = 24
S = 10

mhet_mod_prot_K24 <- read_data(K, A, B, R, S)
mhet_mod_prot_K24_comp <- mhet_mod_prot_K24$result_comp
mhet_mod_prot_K24_xrr <- mhet_mod_prot_K24$result_xrr
mhet_mod_prot_K24_pr <- mhet_mod_prot_K24$prob_reject_all
# mhet_mod_prot_K24_pr
```


```{r}
A = 11.0
B = 16.5
R = 0.01
K = 48
S = 10

mhet_mod_prot_K48 <- read_data(K, A, B, R, S)
mhet_mod_prot_K48_comp <- mhet_mod_prot_K48$result_comp
mhet_mod_prot_K48_xrr <- mhet_mod_prot_K48$result_xrr
mhet_mod_prot_K48_pr <- mhet_mod_prot_K48$prob_reject_all
# mhet_mod_prot_K48_pr
```


```{r}
A = 11.0
B = 16.5
R = 0.01
K = 96
S = 10

mhet_mod_prot_K96 <- read_data(K, A, B, R, S)
mhet_mod_prot_K96_comp <- mhet_mod_prot_K96$result_comp
mhet_mod_prot_K96_xrr <- mhet_mod_prot_K96$result_xrr
mhet_mod_prot_K96_pr <- mhet_mod_prot_K96$prob_reject_all
# mhet_mod_prot_K96_pr
```



```{r}
mhet_mod_prot <- rbind(mhet_mod_prot_K12_pr, 
                       mhet_mod_prot_K24_pr,
                       mhet_mod_prot_K48_pr,
                       mhet_mod_prot_K96_pr)
# mhet_mod_prot
```

```{r}
mhet_mod <- data.frame(rbind(cbind(effect = "No Effect", mhet_mod_null),
                             cbind(effect = "Protective Effect", mhet_mod_prot)
))
mhet_mod
```


\newpage


## Setting 1 - High Heterogenity - High Rate

```{r}
A = 14.5
B = 14.5
R = 0.03
K = 12
S = 10

mhet_high_null_K12 <- read_data(K, A, B, R, S)
mhet_high_null_K12_comp <- mhet_high_null_K12$result_comp
mhet_high_null_K12_xrr <- mhet_high_null_K12$result_xrr
mhet_high_null_K12_pr <- mhet_high_null_K12$prob_reject_all
# mhet_high_null_K12_pr
```

```{r}
A = 14.5
B = 14.5
R = 0.03
K = 24
S = 10

mhet_high_null_K24 <- read_data(K, A, B, R, S)
mhet_high_null_K24_comp <- mhet_high_null_K24$result_comp
mhet_high_null_K24_xrr <- mhet_high_null_K24$result_xrr
mhet_high_null_K24_pr <- mhet_high_null_K24$prob_reject_all
# mhet_high_null_K24_pr
```


```{r}
A = 14.5
B = 14.5
R = 0.03
K = 48
S = 10

mhet_high_null_K48 <- read_data(K, A, B, R, S)
mhet_high_null_K48_comp <- mhet_high_null_K48$result_comp
mhet_high_null_K48_xrr <- mhet_high_null_K48$result_xrr
mhet_high_null_K48_pr <- mhet_high_null_K48$prob_reject_all
# mhet_high_null_K48_pr
```


```{r}
A = 14.5
B = 14.5
R = 0.03
K = 96
S = 10

mhet_high_null_K96 <- read_data(K, A, B, R, S)
mhet_high_null_K96_comp <- mhet_high_null_K96$result_comp
mhet_high_null_K96_xrr <- mhet_high_null_K96$result_xrr
mhet_high_null_K96_pr <- mhet_high_null_K96$prob_reject_all
# mhet_high_null_K96_pr
```

```{r}
mhet_high_null <- rbind(mhet_high_null_K12_pr, 
                        mhet_high_null_K24_pr,
                        mhet_high_null_K48_pr,
                        mhet_high_null_K96_pr)
# mhet_high_null
```


```{r}
A = 11.0
B = 16.5
R = 0.03
K = 12
S = 10

mhet_high_prot_K12 <- read_data(K, A, B, R, S)
mhet_high_prot_K12_comp <- mhet_high_prot_K12$result_comp
mhet_high_prot_K12_xrr <- mhet_high_prot_K12$result_xrr
mhet_high_prot_K12_pr <- mhet_high_prot_K12$prob_reject_all
# mhet_high_prot_K12_pr
```

```{r}
A = 11.0
B = 16.5
R = 0.03
K = 24
S = 10

mhet_high_prot_K24 <- read_data(K, A, B, R, S)
mhet_high_prot_K24_comp <- mhet_high_prot_K24$result_comp
mhet_high_prot_K24_xrr <- mhet_high_prot_K24$result_xrr
mhet_high_prot_K24_pr <- mhet_high_prot_K24$prob_reject_all
# mhet_high_prot_K24_pr
```


```{r}
A = 11.0
B = 16.5
R = 0.03
K = 48
S = 10

mhet_high_prot_K48 <- read_data(K, A, B, R, S)
mhet_high_prot_K48_comp <- mhet_high_prot_K48$result_comp
mhet_high_prot_K48_xrr <- mhet_high_prot_K48$result_xrr
mhet_high_prot_K48_pr <- mhet_high_prot_K48$prob_reject_all
# mhet_high_prot_K48_pr
```


```{r}
A = 11.0
B = 16.5
R = 0.03
K = 96
S = 10

mhet_high_prot_K96 <- read_data(K, A, B, R, S)
mhet_high_prot_K96_comp <- mhet_high_prot_K96$result_comp
mhet_high_prot_K96_xrr <- mhet_high_prot_K96$result_xrr
mhet_high_prot_K96_pr <- mhet_high_prot_K96$prob_reject_all
# mhet_high_prot_K96_pr
```



```{r}
mhet_high_prot <- rbind(mhet_high_prot_K12_pr, 
                        mhet_high_prot_K24_pr,
                        mhet_high_prot_K48_pr,
                        mhet_high_prot_K96_pr)
# mhet_high_prot
```

```{r}
mhet_high <- data.frame(rbind(cbind(effect = "No Effect", mhet_high_null),
                              cbind(effect = "Protective Effect", mhet_high_prot)
))
mhet_high
```



\newpage
## Setting 3  - Low Heterogenity - Mod Rate

```{r}
A = 145
B = 145
R = 0.01
K = 12
S = 10

lhet_mod_null_K12 <- read_data(K, A, B, R, S)
lhet_mod_null_K12_comp <- lhet_mod_null_K12$result_comp
lhet_mod_null_K12_xrr <- lhet_mod_null_K12$result_xrr
lhet_mod_null_K12_pr <- lhet_mod_null_K12$prob_reject_all
# lhet_mod_null_K12_pr
```

```{r}
A = 145
B = 145
R = 0.01
K = 24
S = 10

lhet_mod_null_K24 <- read_data(K, A, B, R, S)
lhet_mod_null_K24_comp <- lhet_mod_null_K24$result_comp
lhet_mod_null_K24_xrr <- lhet_mod_null_K24$result_xrr
lhet_mod_null_K24_pr <- lhet_mod_null_K24$prob_reject_all
# lhet_mod_null_K24_pr
```


```{r}
A = 145
B = 145
R = 0.01
K = 48
S = 10

lhet_mod_null_K48 <- read_data(K, A, B, R, S)
lhet_mod_null_K48_comp <- lhet_mod_null_K48$result_comp
lhet_mod_null_K48_xrr <- lhet_mod_null_K48$result_xrr
lhet_mod_null_K48_pr <- lhet_mod_null_K48$prob_reject_all
# lhet_mod_null_K48_pr
```


```{r}
A = 145
B = 145
R = 0.01
K = 96
S = 10

lhet_mod_null_K96 <- read_data(K, A, B, R, S)
lhet_mod_null_K96_comp <- lhet_mod_null_K96$result_comp
lhet_mod_null_K96_xrr <- lhet_mod_null_K96$result_xrr
lhet_mod_null_K96_pr <- lhet_mod_null_K96$prob_reject_all
# lhet_mod_null_K96_pr
```

```{r}
lhet_mod_null <- rbind(lhet_mod_null_K12_pr, 
                       lhet_mod_null_K24_pr,
                       lhet_mod_null_K48_pr,
                       lhet_mod_null_K96_pr)
# lhet_mod_null
```


```{r}
A = 110
B = 165
R = 0.01
K = 12
S = 10

lhet_mod_prot_K12 <- read_data(K, A, B, R, S)
lhet_mod_prot_K12_comp <- lhet_mod_prot_K12$result_comp
lhet_mod_prot_K12_xrr <- lhet_mod_prot_K12$result_xrr
lhet_mod_prot_K12_pr <- lhet_mod_prot_K12$prob_reject_all
# lhet_mod_prot_K12_pr
```

```{r}
A = 110
B = 165
R = 0.01
K = 24
S = 10

lhet_mod_prot_K24 <- read_data(K, A, B, R, S)
lhet_mod_prot_K24_comp <- lhet_mod_prot_K24$result_comp
lhet_mod_prot_K24_xrr <- lhet_mod_prot_K24$result_xrr
lhet_mod_prot_K24_pr <- lhet_mod_prot_K24$prob_reject_all
# lhet_mod_prot_K24_pr
```


```{r}
A = 110
B = 165
R = 0.01
K = 48
S = 10

lhet_mod_prot_K48 <- read_data(K, A, B, R, S)
lhet_mod_prot_K48_comp <- lhet_mod_prot_K48$result_comp
lhet_mod_prot_K48_xrr <- lhet_mod_prot_K48$result_xrr
lhet_mod_prot_K48_pr <- lhet_mod_prot_K48$prob_reject_all
# lhet_mod_prot_K48_pr
```


```{r}
A = 110
B = 165
R = 0.01
K = 96
S = 10

lhet_mod_prot_K96 <- read_data(K, A, B, R, S)
lhet_mod_prot_K96_comp <- lhet_mod_prot_K96$result_comp
lhet_mod_prot_K96_xrr <- lhet_mod_prot_K96$result_xrr
lhet_mod_prot_K96_pr <- lhet_mod_prot_K96$prob_reject_all
# lhet_mod_prot_K96_pr
```



```{r}
lhet_mod_prot <- rbind(lhet_mod_prot_K12_pr, 
                       lhet_mod_prot_K24_pr,
                       lhet_mod_prot_K48_pr,
                       lhet_mod_prot_K96_pr)
# lhet_mod_prot
```

```{r}
lhet_mod <- data.frame(rbind(cbind(effect = "No Effect", lhet_mod_null),
                             cbind(effect = "Protective Effect", lhet_mod_prot)
))
lhet_mod
```


\newpage


## Setting 1 - High Heterogenity - High Rate

```{r}
A = 145
B = 145
R = 0.03
K = 12
S = 10

lhet_high_null_K12 <- read_data(K, A, B, R, S)
lhet_high_null_K12_comp <- lhet_high_null_K12$result_comp
lhet_high_null_K12_xrr <- lhet_high_null_K12$result_xrr
lhet_high_null_K12_pr <- lhet_high_null_K12$prob_reject_all
# lhet_high_null_K12_pr
```

```{r}
A = 145
B = 145
R = 0.03
K = 24
S = 10

lhet_high_null_K24 <- read_data(K, A, B, R, S)
lhet_high_null_K24_comp <- lhet_high_null_K24$result_comp
lhet_high_null_K24_xrr <- lhet_high_null_K24$result_xrr
lhet_high_null_K24_pr <- lhet_high_null_K24$prob_reject_all
# lhet_high_null_K24_pr
```


```{r}
A = 145
B = 145
R = 0.03
K = 48
S = 10

lhet_high_null_K48 <- read_data(K, A, B, R, S)
lhet_high_null_K48_comp <- lhet_high_null_K48$result_comp
lhet_high_null_K48_xrr <- lhet_high_null_K48$result_xrr
lhet_high_null_K48_pr <- lhet_high_null_K48$prob_reject_all
# lhet_high_null_K48_pr
```


```{r}
A = 145
B = 145
R = 0.03
K = 96
S = 10

lhet_high_null_K96 <- read_data(K, A, B, R, S)
lhet_high_null_K96_comp <- lhet_high_null_K96$result_comp
lhet_high_null_K96_xrr <- lhet_high_null_K96$result_xrr
lhet_high_null_K96_pr <- lhet_high_null_K96$prob_reject_all
# lhet_high_null_K96_pr
```

```{r}
lhet_high_null <- rbind(lhet_high_null_K12_pr, 
                        lhet_high_null_K24_pr,
                        lhet_high_null_K48_pr,
                        lhet_high_null_K96_pr)
# lhet_high_null
```


```{r}
A = 110
B = 165
R = 0.03
K = 12
S = 10

lhet_high_prot_K12 <- read_data(K, A, B, R, S)
lhet_high_prot_K12_comp <- lhet_high_prot_K12$result_comp
lhet_high_prot_K12_xrr <- lhet_high_prot_K12$result_xrr
lhet_high_prot_K12_pr <- lhet_high_prot_K12$prob_reject_all
# lhet_high_prot_K12_pr
```

```{r}
A = 110
B = 165
R = 0.03
K = 24
S = 10

lhet_high_prot_K24 <- read_data(K, A, B, R, S)
lhet_high_prot_K24_comp <- lhet_high_prot_K24$result_comp
lhet_high_prot_K24_xrr <- lhet_high_prot_K24$result_xrr
lhet_high_prot_K24_pr <- lhet_high_prot_K24$prob_reject_all
# lhet_high_prot_K24_pr
```


```{r}
A = 110
B = 165
R = 0.03
K = 48
S = 10

lhet_high_prot_K48 <- read_data(K, A, B, R, S)
lhet_high_prot_K48_comp <- lhet_high_prot_K48$result_comp
lhet_high_prot_K48_xrr <- lhet_high_prot_K48$result_xrr
lhet_high_prot_K48_pr <- lhet_high_prot_K48$prob_reject_all
# lhet_high_prot_K48_pr
```


```{r}
A = 110
B = 165
R = 0.03
K = 96
S = 10

lhet_high_prot_K96 <- read_data(K, A, B, R, S)
lhet_high_prot_K96_comp <- lhet_high_prot_K96$result_comp
lhet_high_prot_K96_xrr <- lhet_high_prot_K96$result_xrr
lhet_high_prot_K96_pr <- lhet_high_prot_K96$prob_reject_all
# lhet_high_prot_K96_pr
```



```{r}
lhet_high_prot <- rbind(lhet_high_prot_K12_pr, 
                        lhet_high_prot_K24_pr,
                        lhet_high_prot_K48_pr,
                        lhet_high_prot_K96_pr)
# lhet_high_prot
```

```{r}
lhet_high <- data.frame(rbind(cbind(effect = "No Effect", lhet_high_null),
                              cbind(effect = "Protective Effect", lhet_high_prot)
))
lhet_high
```


# Make plots

```{r main plot code}
library(ggplot2)
library(tidyr)
library(dplyr)

make_plot <- function(my_data , setting){
  data_long <- gather(my_data, 
                    Method, 
                    prob_reject, 
                    XRR:DL, 
                    factor_key = TRUE) 

data_long <- data_long %>%
  mutate(t1e_fill = if_else((prob_reject <= 0.05) & (effect == "No Effect"), 
                              1 , NA_real_)) %>%   group_by(K, Method) %>%
  fill(t1e_fill) %>%
  mutate(t1e_fill_f = if_else(t1e_fill == 1, TRUE, FALSE)) %>% 
  mutate(t1e_fill_f = replace_na(t1e_fill_f, FALSE))


cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

#jpeg(paste0(setting, ".jpg"))
ggplot(data_long, aes(x = Method, y = as.numeric(prob_reject))) +
  geom_col(aes(fill = K, alpha = t1e_fill_f), position = "dodge") +
  scale_fill_brewer(palette="Set1") +
  #scale_fill_manual(values=cbPalette)+
  #scale_y_continuous(limit = c(0, 1)) +
  ylab("Probability of rejecting H0") +
  facet_wrap(~effect, scales = "free_y") + 
  geom_hline(data = data_long %>% filter(effect == "No Effect"), aes(yintercept= as.numeric(l)),
             linetype="dashed", 
             color = "red") +  
  scale_alpha_manual(values = c(0.4, 1), guide = "none") +
  theme(text = element_text(size = 15)) 

#+
  # geom_text(aes(label = as.numeric(prob_reject)), vjust = 1.5, colour = "white")

  #dev.off()
ggsave(
  paste0(setting, ".jpg"),
  plot = last_plot(), 
  width = 8,
  height = 4)
}
```

\newpage 
# Setting 1 - High hetereogenity, mod


```{r dev = c("jpg")}
make_plot(hhet_mod, setting = "hhet_mod")
```

\newpage
# Setting 1 - High hetereogenity, high

```{r}
make_plot(hhet_high, setting = "hhet_high")
```


\newpage
# Setting 2 - Mod hetereogenity, mod

```{r}
make_plot(mhet_mod, setting = "mhet_mod")
```

\newpage
# Setting 2 - Mod hetereogenity, high

```{r}
make_plot(mhet_high, setting = "mhet_high")
```


\newpage
# Setting 3 - Low hetereogenity, mod

```{r}
make_plot(lhet_mod, setting = "lhet_mod")
```

\newpage
# Setting 3 - Low hetereogenity, high

```{r}
make_plot(lhet_high, setting = "lhet_high")
```





